Explicit Operations on Parametrised Polytopes

### 2018-01-06 dcg-draft.tex
minor change to the proof of Theorem 1

  The proof is completed by noting that, if $\lambda z_1 + (1-\lambda ) z_2 \in\partial S$, then  (\ref{eq:graph:def:p:convexity}) is equivalent to $\mathcal W\bigl(\lambda p_1 + (1-\lambda) p_2 \bigr) \subseteq S$, and by applying the preceding argument for all $\lambda\in (0,1)$ and all $p_1,p_2 \in Y$.
  \qed
% %
% Assume~\eqref{eq:graph:def:p:convexity} holds for $(p_1,z_1),(p_2,z_2)\in\partial\mathscr G(\mathcal W)$.
% %
% Then the extension of the definition of the Minkowski functional (see e.g.~\cite{Rudin:91}) to the graph $\mathscr G(\mathcal W)$,
% \[
% \mu_{\mathscr G(\mathcal W)} \bigl(
% \mathcal W(p), z \bigr)
% := \min_\mu \{\mu \geq 0 : z \in \mu \mathcal W(p)\},
% \]
% yields $\mu_{\mathscr G(\mathcal W)}\left(\mathcal W(\lambda p_1 + (1-\lambda)p_2),\lambda z_1+(1-\lambda)z_2\right)\geq1$ for all $\lambda\in(0,1)$. Therefore $\lambda z_1 + (1-\lambda) z_2$
% lies either outside the set $\mathcal W(\lambda p_1+(1-\lambda)p_2)$ or on its boundary for all $\lambda\in(0,1)$, and hence the set of all possible interpolation points 
% %
% \[
% \begin{split}
%   \lambda \mathcal W(p_1)\oplus (1-\lambda)\mathcal W(p_2) = \{z : z=\lambda z_1 + (1-\lambda) z_2, z_1\in\mathcal  W(p_1),\, z_2\in\mathcal W(p_2)\}
% \end{split}
% \]
% %
% contains the set $\mathcal W(\lambda p_1 + (1-\lambda)p_2)$ for all $\lambda\in(0,1)$.
% %
% Furthermore, since $\lambda(p_1,z_1)+(1-\lambda)(p_2,z_2)\not\in \text{int}(\mathscr G(\mathcal W))$ and both $(p_1,z_1)$ and $(p_2,z_2)$ lie on the boundary, either $z_1-z_2$ or $z_2-z_1$ is outward facing for both $\mathcal W(p_1)$ and $\mathcal W(p_2)$; therefore either $z_1-z_2$ or $z_2-z_1$ lies in both $\mathcal N_{\mathcal W}(p_1,z_1)$ and $\mathcal N_{\mathcal W}(p_2,z_2)$ and hence also in their intersection.

>>>>

  If $\lambda z_1 + (1-\lambda ) z_2 \in\partial S$, then (\ref{eq:graph:def:p:convexity}) is equivalent to $\mathcal W\bigl(\lambda p_1 + (1-\lambda) p_2 \bigr) \subseteq S$, and so proof is completed by applying the preceding argument for all $(p_1,z_1) \in\partial\mathscr G(\mathcal W)$ and $(p_2,z_2)\in\partial\mathscr G(\mathcal W)$, and all $\lambda\in (0,1)$.
  \qed
% %
% Assume~\eqref{eq:graph:def:p:convexity} holds for $(p_1,z_1),(p_2,z_2)\in\partial\mathscr G(\mathcal W)$.
% %
% Then the extension of the definition of the Minkowski functional (see e.g.~\cite{Rudin:91}) to the graph $\mathscr G(\mathcal W)$,
% \[
% \mu_{\mathscr G(\mathcal W)} \bigl(
% \mathcal W(p), z \bigr)
% := \min_\mu \{\mu \geq 0 : z \in \mu \mathcal W(p)\},
% \]
% yields $\mu_{\mathscr G(\mathcal W)}\left(\mathcal W(\lambda p_1 + (1-\lambda)p_2),\lambda z_1+(1-\lambda)z_2\right)\geq1$ for all $\lambda\in(0,1)$. Therefore $\lambda z_1 + (1-\lambda) z_2$
% lies either outside the set $\mathcal W(\lambda p_1+(1-\lambda)p_2)$ or on its boundary for all $\lambda\in(0,1)$, and hence the set of all possible interpolation points 
% %
% \[
% \begin{split}
%   \lambda \mathcal W(p_1)\oplus (1-\lambda)\mathcal W(p_2) = \{z : z=\lambda z_1 + (1-\lambda) z_2, z_1\in\mathcal  W(p_1),\, z_2\in\mathcal W(p_2)\}
% \end{split}
% \]
% %
% contains the set $\mathcal W(\lambda p_1 + (1-\lambda)p_2)$ for all $\lambda\in(0,1)$.
% %
% Furthermore, since $\lambda(p_1,z_1)+(1-\lambda)(p_2,z_2)\not\in \text{int}(\mathscr G(\mathcal W))$ and both $(p_1,z_1)$ and $(p_2,z_2)$ lie on the boundary, either $z_1-z_2$ or $z_2-z_1$ is outward facing for both $\mathcal W(p_1)$ and $\mathcal W(p_2)$; therefore either $z_1-z_2$ or $z_2-z_1$ lies in both $\mathcal N_{\mathcal W}(p_1,z_1)$ and $\mathcal N_{\mathcal W}(p_2,z_2)$ and hence also in their intersection.
